Thermodynamic fragments in magic state theories

### 2020-11-13 magic_paper.tex
Cleaned up Lorenz curve section, added new notation

\subsubsection{Standard Lorenz curves in terms of binomial distributions}
\textbf{Note:} We assume that the number of copies $n$ is even throughout.

The Lorenz curve $\lc{\noisysn}{\frac{1}{d}\id}$ consists of $n+1$ line segments, connecting at $n$ points, called \emph{elbows}, between the endpoints $(0,0)$ and $(1,1)$, as illustrated in~\cref{fig:lcsu_elbows}. 
\begin{figure}[b]
    \centering
    \includegraphics[scale=0.5]{figs/lccalcdiagram.pdf}
    \caption{\textbf{Anatomy of Strange state Lorenz curve}
    There are $n$ ``elbows'' in this Lorenz curve of an $n$-copy Strange state.
    Labels $k, k'$ indicate two elbows for the $n=4$ case.
    Their coordinates are given in~\cref{eq:lcsu_elbows}.
    }
    \label{fig:lcsu_elbows}
\end{figure}
We denote the Lorenz curve maximum as the $k_\star$-th point.
It occurs at 
\begin{align}\label{eq:lcsu_max}
	x_{k_\star} &= \frac{1}{2}\left(1 + \left( \frac{7}{9} \right)^n \right), \\
	L_{k_\star} &\equiv \lc{\noisysn}{\frac{1}{d}\id}(x_{k_\star}) = \frac{1}{2}\left (1 + \left(\frac{5}{3}-\frac{8}{9}\epsilon\right)^n \right),
\end{align}
with $k_\star = n/2$.
The coordinates of the standard Lorenz curve for a gien number of copies $n$ and noise level $\epsilon$ can be directly expressed in terms of $\Phi_+, \Phi_-$, for all $m$, $n$ the number of copies and some fixed $p \equiv p(\epsilon)$.

The Wigner distribution of the qutrit maximally mixed state $\id/3$ is the uniform distribution $\bm{1}/9$.
The Wigner distribution of the 1-copy noisy Strange state $\rho_{\rm{S}}(\epsilon)$ in the unital fragment is a permutation of 8 positive components ($w_+$) and 1 negative ($w_-$) with
\begin{align}
	w_+ &= \frac{1}{6} - \frac{1}{18}\epsilon \\
	w_- &= -\frac{1}{3} + \frac{4}{9}\epsilon.
\end{align}
They are depicted in~\cref{fig:noisys}.
\begin{figure}[t]
    \centering
    \includegraphics[scale=0.7]{figs/noisys.pdf}
    \caption{\textbf{Wigner components of the noisy Strange state.} 
    In the interval $0 \leq \epsilon < 3/7$, the negative component is larger than the positive components.
    At $\epsilon = 3/7$ the Wigner distribution is $(-\frac{1}{7},\frac{1}{7},\dots,\frac{1}{7})$.
    In the interval $3/7 < \epsilon < 3/4$, the positive components are larger than the negative component.
    In the interval $3/4 \leq \epsilon \leq 1$, there is no negativity.
    }
    \label{fig:noisys}
\end{figure}
The $n+1$ distinct Wigner components ($w_j$) of $\noisysn$ along with their multiplicities ($c_j$) are given in~\cref{tab:lcsu_w}.
\begin{table}[t]                           
 \centering
 \begin{tabular}{c|c|c|c}
 $\epsilon$ & $j$ & $\left[0, \frac{n}{2}\right]$ & $\left[\frac{n}{2} + 1, n \right]$ \\ [0.5ex] 
 \hline
  & $w_{j}$ & $w_+^{2j}w_-^{n-2j}$ & $w_+^{n-2j}w_-^{2j}$  \\
  $0\leq \epsilon < \frac{3}{7}$ & & & \\
  & $c_{j}$ & $8^{2j}\binom{n}{2j}$ & $8^{n-2j}\binom{n}{2j}$ \\
 \hline
  & $w_{j}$ & $w_+^{n-2j}w_-^{2j}$ & $w_+^{2j}w_-^{n-2j}$  \\
  $\frac{3}{7} \leq \epsilon < \frac{3}{4} $ & & & \\
  & $c_{j}$ & $8^{n-2j}\binom{n}{2j}$ & $8^{2j}\binom{n}{2j}$
\end{tabular}
 \caption{Wigner components of $\rho_{\rm{S}}^{\otimes n}(\epsilon)$. The multiplication $2j$ is modulo $(n+1)$.}
 \label{tab:lcsu_w}
\end{table}

@@

We are now in a position to express Lorenz curve coordinates in terms of phi distributions,
\begin{equation}\label{x_coord_elb}
	x_k(n, \epsilon) = 
	\begin{cases}
		\Phi_+(k;n,p_x),\\
		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ even}, \\
		x_{k_\star} + \Phi_-(k;n,1-p_x),\\
		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ odd}, \\
	\end{cases}	
\end{equation}
and
\begin{equation}\label{lc_coord_elb}
	L_k(n, \epsilon) = 
	\begin{cases}
		\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+(k;n,p_L),\\
		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ even}, \\
		L_{k_\star} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-(k;n,1-p_L),\\
		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ odd}. \\
	\end{cases}	
\end{equation}

@@

\subsubsection{Lorenz curve comparison}
Consider the magic state conversion,
\begin{equation}\label{eq:su_conversion}
	\noisysn \xrightarrow{\E \in \O_{\id/d}} \rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}.
\end{equation}
Pointwise comparison of the initial and final state Lorenz curves is non-trivial, since the elbows of the curves do not align vertically.
The initial state Lorenz curve consists of
\begin{equation}
	1 + \sum_{j=0}^{n} c_j = d^{2n} + 1
\end{equation}
points with $x$-coordinates incrementing by $\frac{1}{9^n}$ which we denote as the set 
\begin{equation}
X \coloneqq \left\{ \frac{k}{d^{2n}} \right\}_{0 \leq k \leq d^{2n}}.
\end{equation}

The final state Lorenz curve consists of $9^k (< 9^n)$ points, however, since we work in the unital fragment, the maximally mixed state $\frac{1}{d}\id$ is free, so can add in arbitrary many copies to the final state. 
This addition does not change the total Lorenz curve of the state, but merely increases the resolution on the $x$-axis. 
We thus want to compute the Lorenz curve of the state
\begin{equation}
\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k} \otimes \left( \frac{1}{d}\id\right)^{\otimes(n-k)},
\end{equation}
with transformed Wigner components 
\begin{equation}
w_j^\prime = \frac{1}{d^{2(n-k)}}w_j,
\end{equation}
and multiplicities $c_j^\prime = d^{2(n-k)}c_j$, where $w_j, c_j$ are given in~\cref{tab:lcsu_w} for $j=0,\dots,k$. 
\ddd{[DJ: You've been too sloppy and rushed here. Give the explicit definition of $w'_j$. You've hit a problem almost certainly because you are not handling this technical bit carefully and explicitly - it is crucial, so really unpack it slowly!]} \nick{I don't think it gets more explicit, you just split the line segments uniformly into $d^{2(n-k)}$ segments of length equal to $1/d^{2(n-k)}$ of the total length.}

Let's look at an example in~\cref{fig:lc_compare}.
The Lorenz curve of the final state $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2}$ remains the same when we rewrite the state as $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2} \otimes (\tfrac{1}{3} \id)^{\otimes 2}$, but now it consists of $9^4$ points with the same $x$-coordinates as the initial state.
The line segment between elbows $x_0 = 0$ and $x_1 = 1/9^2$ consists only of its endpoints for state $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2}$.
However, for state $\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes 2} \otimes \left( \tfrac{1}{3} \id\right)^{\otimes 2}$ it consists of $82$ points with coordinates $(k/9^4, kw_0)$ for $k=0,\dots,9^2$.
The same reasoning applies on all three line segments comprising the Lorenz curve.
\begin{figure}[t]
    \centering
    \includegraphics[scale=0.6]{figs/lc_compare.pdf}
    \caption{\textbf{Example of Lorenz curve comparison.} 
    The upper Lorenz curve (blue / $n=4$ and $\epsilon = 0.20$) is always higher than the lower Lorenz curve (red / $k=2$ and $\epsilon_\tau = 0.05$).
    }
    \label{fig:lc_compare}
\end{figure}
Therefore, we can compare the curves pointwise with $9^n + 1$ inequalities of the form
\begin{equation}\label{eq:lc_pointwise}
\lc{\noisysn}{\frac{1}{d}\id}(x) \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x)
\end{equation}
for all $x \in X$.

According to~\cref{thm:dmajor}, a necessary condition for $\rho \xrightarrow{\E \in \O_\sigma} \tau$ is that $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$.
We can reduce the inequalities in~\cref{eq:lc_pointwise} significantly with the following result.
\begin{theorem}\label{thm:elbows}
	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$-fragment.

@@

Returning to~\ref{eq:su_conversion}, the $k$ independent necessary constraints are
\begin{align}
\lc{\noisysn}{\frac{1}{d}\id}(x_1) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_1), \nonumber\\
\lc{\noisysn}{\frac{1}{d}\id}(x_2) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_2), \nonumber\\
&\vdotswithin{=} \nonumber\\
\lc{\noisysn}{\frac{1}{d}\id}(x_k) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_k), \nonumber
\end{align}
where $x_1, x_2, \dots, x_k \in T \subset X$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).

The RHSs can be calculated directly by~\cref{lc_coord_elb}, but the LHSs do not correspond to elbows.
To calculate $\lc{\noisysn}{\frac{1}{d}\id}(x_j)$ for $j=1,\dots,k$, we first need to identify the elbow of the curve just before $x_j$.
Let $R \coloneqq \{y_0, y_1, \dots, y_n, y_{n+1}\} \subset X$ be the elbows of $\lc{\noisysn}{\frac{1}{d}\id}(x)$.
Then, the elbow index just before $x_j$ is
\begin{equation}
	J = \max{\{i: y_i \leq x_j \}}.
\end{equation}
The slope from the $J$-th elbow to point $(x_j, \lc{\noisysn}{\frac{1}{d}\id}(x_j)$ is given by the $(J+1)$-th Wigner component, so that the LHS can be calculated as 
\begin{equation}\label{calc_lhs}
	L_J + d^{2n}(x_j - x_J)w_{J+1}.
\end{equation}
This is illustrated in~\cref{fig:lc_compare}, where we check the constraint at $x_2 = 0.8025$.
Using~\cref{lc_coord_elb}, we find that $\lc{\rho_{\rm{S}}(\epsilon_\tau)^{\otimes 2}}{\frac{1}{d}\id}(x_2) = 1.8158$, while expression~\cref{calc_lhs} gives $\lc{\rho_{\rm{S}}(\epsilon)^{\otimes 4}}{\frac{1}{d}\id}(x_2) = 2.235$.

\null\newpage
\null\newpage

The experiment is described by binomial statistics and we define the left and ``right'' tails of the cumulative binomial distribution,
\begin{align}
	\Phi_\ell(m; n, p) &\coloneqq \sum\limits_{j=0}^m \binom{n}{j} p^j (1-p)^{n-j}, \label{eq:phi}\\
	\Phi_r(m; n, p) &\coloneqq \sum\limits_{j=m}^n \binom{n}{j} p^j (1-p)^{n-j}, \label{eq:phir}
\end{align}
where $m\in [0,n]$.

They are related by the symmetry between the left tail of a $p$-coin distribution and the right tail of a $(1-p)$-coin distribution,
\begin{equation}\label{eq:phil2phir}
	\Phi_\ell(m; n, p) = \Phi_r(n-m; n, 1-p),\ m\in [0,n],
\end{equation}
as well as the normalisation condition,
\begin{equation}
	\Phi_\ell(m; n, p) + \Phi_r(m+1; n, p) = 1,\ m\in [0,n-1].
\end{equation}

Equivalently, we get
\begin{align}
	\Phi_\ell(m; n, p) + \Phi_\ell(n-m-1; n, 1-p) &= 1,\ m\in [0,n-1], \label{eq:reversephi}\\
	\Phi_r(m; n, p) + \Phi_r(n-m+1; n, 1-p) &= 1,\ m\in [1,n]. \label{eq:reversephir}
\end{align}

Bounds on the tails of a cumulative binomial distribution can be expressed in terms of the classical relative entropy between a $p$-coin and a $q$-coin,
\begin{equation}\label{eq:ent_rel}
	\ent{p}{q} \coloneqq p \log{\frac{p}{q}} + (1-p) \log{\frac{1-p}{1-q}}.
\end{equation}
This entropy satisfies the identity
\begin{equation}
	\ent{p}{q} = \ent{1-p}{1-q}.
\end{equation}
We can now derive entropic bounds on binomial cumulative distributions~\cite{cit:ash}.
\begin{lemma}\label{lem:phir_bounds}
	Given fixed $n>0$ and $p$, $\Phi_r$ satisfies the following bounds:
	\begin{align*}
		\begin{split}
		&\text{1. } \Phi_r(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
		&\text{2. } \Phi_r(m; n, p) \leq 2^{-n\ents},\ m\in [np,n] \\
		&\text{3. } \Phi_r(m; n, p) \leq 1 - \left[ 8(m-1)\left(1-\frac{m-1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m-1}{n}}{p}}, \\
		&\hspace{14pt} m\in [2,n]
		\end{split}
		\\
		&\text{4. } \Phi_r(m; n, p) \geq 1 - 2^{-n\ent{\frac{m-1}{n}}{p}},\ m\in [2,np+1]
	\end{align*}

	The asymptotic behaviour of $\Phi_r$ is determined by the relative entropy, 
	\begin{equation}
		\lim_{n\rightarrow\infty}{-\frac{1}{n}\log{\Phi_r(m; n, p)} = \ent{\frac{m}{n}}{p}},\ m\in [np,n]
	\end{equation}
\end{lemma}
\begin{proof}
	For bound (1), note that
	\begin{align*}
		\Phi_r(m; n, p) &= \sum\limits_{j=m}^n \binom{n}{j} p^j (1-p)^{n-j} \\
						   &\geq \binom{n}{m} p^{m} (1-p)^{n-m} \\
						   &\geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{nS\left(\frac{m}{n}\right)} p^{m} (1-p)^{n-m} \\
						   &= \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents}.
	\end{align*}
	The first inequality follows from the positivity of the terms in the series, the second from~\cref{lem:comb_bounds} and the equality from the entropy definitions in~\cref{eq:ent,eq:ent_rel}

	For bound (2), consider a binomial random variable $X = \sum_{i=1}^N$, where $X_i$ takes the values 1, 0 with probabilities $p$ and $1-p$ respectively.
	Then we have
	\begin{align*}
		\Phi_r(m; n, p) &= P(X \geq m) = P\left(2^{rX} \geq 2^{rm}\right) \\
						   &\leq 2^{-rm} E\left(2^{rX}\right) = 2^{-rm + n\log{(1-p+pe^r)}} \\
						   &\leq 2^{-n\ents}.
	\end{align*}
	The first inequality holds for any discrete random variable $X$ with $r \geq 0$, while the second inequality involves maximisation of the exponent which occurs at $e^r = \frac{m(1-p)}{(n-m)p}$ (a non-negative $r$ exists if $np \leq m$).

	Bound 3 follows from bound 1 and~\cref{eq:reversephir}. Bound 4 follows from bound 2 and~\cref{eq:reversephir}.

	The asymptotic limit is a direct consequence of the squeeze theorem.
\end{proof}

\begin{lemma}\label{lem:phil_bounds}
	Given fixed $n>0$ and $p$, $\Phi_\ell$ satisfies the following bounds:
	\begin{align*}
		\begin{split}
		&\text{1. } \Phi_\ell(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
		&\text{2. } \Phi_\ell(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
		&\text{3. } \Phi_\ell(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
		&\hspace{14pt} m\in [0,n-2]
		\end{split}
		\\
		&\text{4. } \Phi_\ell(m; n, p) \geq 1 - 2^{-n\ent{\frac{m+1}{n}}{p}},\ m\in [np+1,n-2]
	\end{align*}

	The asymptotic behaviour of $\Phi_\ell$ is determined by the relative entropy,
	\begin{equation}
		\lim_{n\rightarrow\infty}{-\frac{1}{n}\log{\Phi_r(m; n, p)} = \ent{\frac{m}{n}}{p}},\ m\in [0,np]
	\end{equation}
\end{lemma}
\begin{proof}
	This lemma is a direct consequence of~\cref{lem:phir_bounds} and~\cref{eq:phil2phir}.
\end{proof}

We now define the alternating counterpart of the left tail distribution,
\begin{equation}\label{eq:phialt}
	\Phi_\ell^{\rm{alt}}(m; n, p) \coloneqq \sum\limits_{j=0}^m \binom{n}{j} (-p)^j (1-p)^{n-j},
\end{equation}
where $m\in [0,n]$.
$\Phi_\ell^{\rm{alt}}$ is \emph{not} the cumulative distribution of any random variable.
It is upper bounded by $\Phi_\ell$,
\begin{equation}\label{eq:phialt_bound}
	\abs{\Phi_\ell^{\rm{alt}}(m; n, p)} \leq \Phi_\ell(m; n, p),\ m\in [0,n]
\end{equation}
with equality iff $m=0$.

We further define the two balanced combinations of $\Phi_\ell, \Phi_\ell^{\rm{alt}}$ for all $m\in [0,n]$,
\begin{align}	
	\Phi_+(m; n, p) &\coloneqq \frac{1}{2} \left( \Phi_\ell(m; n, p) + \Phi_\ell^{\rm{alt}}(m; n, p) \right), \\
	\Phi_-(m; n, p) &\coloneqq \frac{1}{2} \left( \Phi_\ell(m; n, p) - \Phi_\ell^{\rm{alt}}(m; n, p) \right), \\
	\Phi(m; n, p) &\coloneqq \label{eq:phi}
	\begin{cases}
		\Phi_+(m; n, p),\ \text{for even }m\in[0,n] \\
		\Phi_-(m; n, p),\ \text{for odd }m\in[0,n].
	\end{cases}
\end{align}
\begin{lemma}\label{lem:phi_bounds}
	Given fixed $n>0$ and $p$, $\Phi$ satisfies the following bounds:
	\begin{align*}
		\begin{split}
		&\text{1. } \Phi(m; n, p) \geq \left[ 8m\left(1-\frac{m}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ents},\ m\in [1,n-1] \\
		&\text{2. } \Phi(m; n, p) \leq 2^{-n\ents},\ m\in [0,np] \\
		&\text{3. } \Phi(m; n, p) \leq 1 - \left[ 8(m+1)\left(1-\frac{m+1}{n}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{m+1}{n}}{p}}, \\
		&\hspace{14pt} m\in [0,n-2]
		\end{split}
	\end{align*}
\end{lemma}
\begin{proof}
	Bound 1 follows directly from~\cref{lem:comb_bounds}.

>>>>

\subsubsection{Standard Lorenz curves in terms of binomial distributions}

The Wigner distribution of the qutrit maximally mixed state $\id/3$ is the uniform distribution $\bm{1}/9$.
The Wigner distribution of the 1-copy noisy Strange state $\rho_{\rm{S}}(\epsilon)$ in the unital fragment is a permutation of 8 positive components ($w_+$) and 1 negative ($w_-$) with
\begin{align}
	w_+ &= \frac{1}{6} - \frac{1}{18}\epsilon \\
	w_- &= -\frac{1}{3} + \frac{4}{9}\epsilon.
\end{align}
They are depicted in~\cref{fig:noisys}.
\begin{figure}[t]
    \centering
    \includegraphics[scale=0.7]{figs/noisys.pdf}
    \caption{\textbf{Wigner components of the noisy Strange state.} 
    In the interval $0 \leq \epsilon < 3/7$, the negative component is larger than the positive components.
    At $\epsilon = 3/7$ the Wigner distribution is $(-\frac{1}{7},\frac{1}{7},\dots,\frac{1}{7})$.
    In the interval $3/7 < \epsilon < 3/4$, the positive components are larger than the negative component.
    In the interval $3/4 \leq \epsilon \leq 1$, there is no negativity.
    }
    \label{fig:noisys}
\end{figure}
The $n+1$ distinct Wigner components ($w_j$) of $\noisysn$ along with their multiplicities ($c_j$) are given in~\cref{tab:lcsu_w}.
\begin{table}[b]                           
 \centering
 \begin{tabular}{c|c|c|c}
 $\epsilon$ & $j$ & $\left[0, \frac{n}{2}\right]$ & $\left[\frac{n}{2} + 1, n \right]$ \\ [0.5ex] 
 \hline
  & $w_{j}$ & $w_+^{2j}w_-^{n-2j}$ & $w_+^{n-2j}w_-^{2j}$  \\
  $0\leq \epsilon < \frac{3}{7}$ & & & \\
  & $c_{j}$ & $8^{2j}\binom{n}{2j}$ & $8^{n-2j}\binom{n}{2j}$ \\
 \hline
  & $w_{j}$ & $w_+^{n-2j}w_-^{2j}$ & $w_+^{2j}w_-^{n-2j}$  \\
  $\frac{3}{7} \leq \epsilon < \frac{3}{4} $ & & & \\
  & $c_{j}$ & $8^{n-2j}\binom{n}{2j}$ & $8^{2j}\binom{n}{2j}$
\end{tabular}
 \caption{Wigner components of $\rho_{\rm{S}}^{\otimes n}(\epsilon)$. The multiplication $2j$ is modulo $(n+1)$.}
 \label{tab:lcsu_w}
\end{table}

@@

We are now in a position to express Lorenz curve coordinates in terms of phi distributions,
\begin{equation}\label{eq:x_coord_elb}
	x_k(n, \epsilon) = 
	\begin{cases}
		\Phi_+(k;n,p_x),\\
		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ even}, \\
		x_{k_\star} + \Phi_-(k;n,1-p_x),\\
		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ odd}, \\
	\end{cases}	
\end{equation}
and
\begin{equation}\label{eq:lc_coord_elb}
	L_k(n, \epsilon) = 
	\begin{cases}
		\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+(k;n,p_L),\\
		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ even}, \\
		L_{k_\star} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-(k;n,1-p_L),\\
		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ odd}. \\
	\end{cases}	
\end{equation}

@@

\subsubsection{Pointwise Lorenz curve comparison}

In this subsection, we obtain explicit coordinates for all points on the Lorenz curve.

Consider the $\epsilon$-noisy, $n$-copy Strange state
\begin{equation}
    \noisysn = \left( (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \frac{1}{3}\id \right)^{\otimes n},
\end{equation}
with Wigner distribution
\begin{equation}
	\begin{split}
		\W{\noisysn} &= \left( \overbrace{\frac{1}{6} - \frac{1}{18}\epsilon, \dots, \frac{1}{6} - \frac{1}{18}\epsilon}^8, \overbrace{-\frac{1}{3} + \frac{4}{9}\epsilon}^1 \right)^{\otimes n} \\
		&= \rm{W}^+_{\noisysn} + \rm{W}^-_{\noisysn},
	\end{split}
\end{equation}
where we split non-negative and negative components into $\rm{W}^+_{\noisysn}$ and $\rm{W}^-_{\noisysn}$.

As a simple example, we split the Wigner distribution of state $\rho_{\rm{S}}(0)^{\otimes 2}$,
\begin{equation*}
	\begin{split}
    &\rm{W}^+_{\rho_{\rm{S}}(0)^{\otimes 2}} = \left( \overbrace{\left( -\frac{1}{3} \right)^2}^1, \overbrace{\left( \frac{1}{6} \right)^2, \dots, \left( \frac{1}{6} \right)^2}^{64} \right) \text{ and } \\
    &\rm{W}^-_{\rho_{\rm{S}}(0)^{\otimes 2}} = \left( \overbrace{ -\frac{1}{3} \cdot \frac{1}{6}, \dots, -\frac{1}{3} \cdot \frac{1}{6}}^{16} \right)
    \end{split}
\end{equation*}

For now, we restrict to the non-negative Wigner components $\rm{W}^+_{\noisysn}$ [i.e. the ``LHS of the Lorenz curve''] and we drop superscript $+$ for clarity.
Assume: 
\begin{itemize}
    \item $n$ is even [ensures Lorenz curve coordinates can be expressed in terms of $\Phi_{\pm}$ distributions];
    \item $0 \leq \epsilon \leq \frac{3}{7}$ [ensures closed-form expressions for Lorenz curve coordinates];
\end{itemize}
There are $\frac{n}{2}+1$ distinct non-negative components in the Wigner distribution $\W{\noisysn}$.\\

We can rewrite the non-negative part of the Wigner distribution $\W{\noisysn}$ in a compact form, by simply listing the distinct Wigner components $w(k; n, \epsilon)$ along with their multiplicities $m(k; n)$:
\begin{align}
    &{\W{\noisysn}} = \\ 
    &\big\{\left( m_k, w_k \right)\big\}_{k=0,\dots,n/2} = \nonumber\\ 
    &\big\{\left( m(k; n), w(k; n, \epsilon) \right)\big\}_{k=0,\dots,n/2} = \nonumber\\
    &\left\{ \left( 8^{n-2k}\binom{n}{2k}, \left( \frac{1}{6} - \frac{1}{18}\epsilon \right)^{2k}\left( -\frac{1}{3} + \frac{4}{9}\epsilon \right)^{n-2k} \right) \right\}_{k=0,\dots,n/2}. \nonumber
\end{align}

The expressions for the Lorenz curve elbows in the unital fragment are then known:
\begin{align}
    &{\rm{L}_{\noisysn}} = \\
    &\big\{\left( x_k, L_k \right)\big\}_{k=0,\dots,n/2} = \nonumber\\
    &\big\{\left( x(k; n), L(k; n, \epsilon) \right)\big\}_{k=0,\dots,n/2} = \nonumber\\
    &\left\{ \left( \frac{1}{9^n}\sum\limits_{j=0}^k m_j, \sum\limits_{j=0}^k m_j w_j \right) \right\}_{k=0,\dots,n/2} = \nonumber\\
    &\left\{ \left( \Phi_+\left(2k;n,\frac{8}{9}\right), \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+\left(2k;n,4\frac{3-\epsilon}{15-8\epsilon}\right) \right) \right\}_{k=0,\dots,n/2}. \nonumber
\end{align}
We include the origin in the Lorenz curve as it does not arise from the above expressions, denoting it by $(x_{-1}, L_{-1}) \coloneqq (0,0)$.

We can get explicit expressions for all $\frac{1}{2}(7^n + 9^n)$ points of the Lorenz curve, using a two-index parameterisation:
\begin{align}
    x_{k,\alpha} &= \left( 1-\frac{\alpha}{m_k} \right) x_{k-1} + \frac{\alpha}{m_k} x_k \label{eq:x}\\
    L_{k,\alpha} &= \left( 1-\frac{\alpha}{m_k} \right) L_{k-1} + \frac{\alpha}{m_k} L_k \label{eq:l}\\
    &\text{for } k=0,\dots,\frac{n}{2} \text{ and } \alpha = 1,\dots,m_k. \nonumber
\end{align}

As a simple example, we plot the Lorenz curve of state $\rho_{\rm{S}}(0)^{\otimes 2}$,
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.6]{figs/lcpoints.pdf}
    \caption{\textbf{All points on the Lorenz curve are uniformly distributed.}
    \cref{eq:x,eq:l}) capture the coordinates of all points up to the maximum.
    }
    \label{fig:lc}
\end{figure}

Consider now the state 
\begin{equation}
    \rho(m, \epsilon, s) = \rho_{\rm{S}}(\epsilon)^{\otimes m} \otimes \left( \frac{1}{3}\id \right)^{\otimes s}.
\end{equation}

Tensoring with the maximally mixed state keeps the Lorenz curve unchanged, but increases the resolution of (the uniformly distributed) points.
The new point coordinates are given by:
\begin{align}
    x_{k,\alpha, \beta} &= \left( 1-p_{k,\alpha, \beta}\right) x_{k-1} + p_{k,\alpha, \beta} x_k \\
    L_{k,\alpha, \beta} &= \left( 1-p_{k,\alpha, \beta} \right) L_{k-1} + p_{k,\alpha, \beta} L_k, \\
    &\text{where } p(k, \alpha, \beta) = \frac{(\alpha-1)9^s + \beta}{9^s m_k} \\
    &\text{for } k=0,\dots,\frac{n}{2},\ \alpha = 1,\dots,m_k \text{ and } \beta = 1,\dots,9^s. \nonumber
\end{align}

We can unify the indices, by introducing a single index
\begin{equation}
    i(k,\alpha,\beta) \coloneqq \beta + \left[ (\alpha-1) + \sum_{j=0}^{k-1} 8^{m-2j}\binom{m}{2j} \right]9^s,
\end{equation}
so that $i=1,2,\dots, \frac{1}{2}(7^{m+s} + 9^{m+s})$.
The $\frac{m}{2}$ elbows correspond to $\beta=0,\ \alpha=1$.
This index function is bijective.

\section*{Strange state Lorenz curve comparison in the unital fragment}

Consider the Strange state purification process in the unital fragment,
\begin{equation}\label{eq:su_conversion}
    \noisysn \xrightarrow{\mathcal{O}_{\id/d}} \rho_{\rm{S}}(m, \epsilon', s).
\end{equation}
In order to get Lorenz curve constraints on this state conversion, we need to match up the indices for the two states.
We use non-primed indices for the initial state and primed indices for the target state,
\begin{align}
    i(k, \alpha) &= (\alpha-1) + \sum_{j=0}^{k-1} 8^{n-2j}\binom{n}{2j}, \\
    i'(k',\alpha',\beta') &= \beta' + \left[ (\alpha'-1) + \sum_{j'=0}^{k'-1} 8^{m-2j'}\binom{m}{2j'} \right]9^s,
\end{align}

The question is: \emph{Given a triplet $(k', \alpha', \beta')$, what is the tuple $(k, \alpha)$ such that $i(k, \alpha) = i'(k',\alpha',\beta')$?}

\begin{theorem}\label{thm:elbows}
	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$-fragment.

@@

Returning to~\cref{eq:su_conversion}, the $k$ independent necessary constraints are
\begin{align}
\lc{\noisysn}{\frac{1}{d}\id}(x_{1,0,0}) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_{1,0,0}), \nonumber\\
\lc{\noisysn}{\frac{1}{d}\id}(x_{2,0,0}) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_{2,0,0}), \nonumber\\
&\vdotswithin{=} \nonumber\\
\lc{\noisysn}{\frac{1}{d}\id}(x_{m,0,0}) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_{m,0,0}), \nonumber
\end{align}
where $x_{1,0,0}, x_{2,0,0}, \dots, x_{m,0,0} \in T \subset X$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).
